\papertitle

### 2023-11-27 src/tex/ms.tex
Mention difference between overlapping/non

Eqn.~\ref{equ:varmsd} gives the variance of the mean squared displacement for a single particle considering a single time-origin.
We can obtain improved statistics by averaging over statistically equivalent observed squared displacements (see Eqn.~2 in the main text), which can be achieved by averaging over mobile particles or by averaging over time origins.
This averaging over equivalent observations reduces the variance in the observed MSD to
\begin{equation}
    \var{\oMSDn} = \frac{2n^2\kappa^4}{\nind{n}},
\label{equ:der_var}
\end{equation}
where $\nind{n}$ is the total number of statistically independent squared displacements that contribute to $\oMSDi$.
In the long-time limit, $\nind{n}$ is given by the product of the number of mobile particles and the number of numerically-independent sub-trajectories of length $i$ in our simulation trajectory.
Note that $\nind{n}$ considers numerically-independent sub-trajectories, since mutually overlapping time-windows give correlated squared displacements.

>>>>

Eqn.~\ref{equ:varmsd} gives the variance of the mean squared displacement for a single particle considering a single time-origin.
We can obtain improved statistics by averaging over statistically equivalent observed squared displacements (see Eqn.~2 in the main text), which can be achieved by averaging over mobile particles or by averaging over time origins.
This averaging over equivalent observations reduces the variance in the observed MSD to
\begin{equation}
    \var{\oMSDn} = \frac{2n^2\kappa^4}{\nind{n}},
\label{equ:der_var}
\end{equation}
where $\nind{n}$ is the total number of statistically independent (non-overlapping) squared displacements that contribute to $\oMSDi$.
In the long-time limit, $\nind{n}$ is given by the product of the number of mobile particles and the number of numerically-independent sub-trajectories of length $i$ in our simulation trajectory.
Note that $\nind{n}$ considers numerically-independent sub-trajectories, since mutually overlapping time-windows give correlated squared displacements.
Where overlapping time-windows are used, Eqn.~\ref{equ:der_var} approximates the observed variance (the variance for overlapping and non-overlapping samples are not the same) with accuracy that increases as a function of time-interval length. 
This leads to the approximation in Eqn.~\ref{equ:varestMSD}.
